---
html_document:
  theme: flatly
author: "Miguel-Angel Canela, IESE Business School"
date: "January 17, 2018"
output:
  html_document: default
title: "Discussion [1]"
---
### Assignment 1

*With the function `sample` we can extract random samples from a given set, with or without replacement. For instance, with `x <- sample(c("H","T"), size=1000, replace=T)`, we can simulate a sequence of 1,000 coin tosses. Create a function that measures the length of longest run of heads in a sequence of coin tosses. How is the sampling distribution of this statistic?*

```{r}
runMax <- function(i) {
  x <- sample(c(1, 0), size=1000, replace=T)
  y <- x[1]
  for(i in 2:1000) y[i] <- x[i]*(y[i - 1] + x[i])
  return(max(y))
}
table(sapply(1:1000, runMax))
```

### Assignment 2

*For a pair of positive integers `x` and `y`, we can get the reminder of the division of `x` by `y` by doing `x %% y`. Exploit this to create a function that checks whether a positive integer is prime (i.e. it returns `TRUE` for primes and `FALSE` for composites).*

```{r}
numDivisors <- function(n) sum(n %% (1:n) == 0)
numDivisors(28)
isPrime <- function(n) numDivisors(n) == 2
isPrime(23)
isPrime(15)
```


### Assignment 3

*For any positive integer `n`, the polynomial `x^n + x - 1` has a root in the interval `[0, 1]`. You can check this, for instance, for `n = 4`, creating `x <- seq(0, 1, by=0.001)`, which is a partition of the interval into 1,001 subintervals, defining `y <- x^4 + x - 1` and plotting with `plot(y ~ x, type="l")`. Create a function of `n` that returns the root of the polynomial, up to the third digit.*

```{r}
x <- seq(0, 1, by=0.001)
solution <- function(n) {
  y <- x^n + x -1
  y1 <- max(y[y < 0])
  y2 <- min(y[y > 0])
  x1 <- x[y == y1]
  x2 <- x[y == y2]
  return(mean(x1, x2))
}
solution(2)
```

